Data Science Applied to Ag - Final Project - ML

### 2025-04-26 code/Draft_script.qmd
d

@@

#parallel processing
registerDoParallel(cores = parallel::detectCores()-1)

@@

stopImplicitCluster()

@@

```{r final_spec_fit}
final_spec <- boost_tree(
  trees = best_r2$trees,           # Number of boosting rounds (trees)
  tree_depth = best_r2$tree_depth, # Maximum depth of each tree
  min_n = best_r2$min_n,           # Minimum number of samples to split a node
  learn_rate = best_r2$learn_rate  # Learning rate (step size shrinkage)
) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

@@

-R2 & RMSE =

-best_r2_pct_loss =

-best_r2_one_std_error =

-best_rmse_pct_loss =

-best_rmse_one_std_err =

@@

```{r}
final_fit %>%
  collect_predictions() %>%
  ggplot(aes(x = yield,
             y = .pred)) +
  geom_point() +
  geom_abline() +
  geom_smooth(method = "lm") +
  scale_x_continuous(limits = c(20, 40)) +
  scale_y_continuous(limits = c(20, 40)) 
```

@@

rf_spec <- 
  # Specifying random forest as our model type, asking to tune the hyperparameters
  rand_forest(trees = tune(),
              mtry = tune() #both "trees" and "mtry" are model-type level hyperparameters, meaning that we fine tune "trees" and "mtry" inside "rand_forest()"
              ) %>%
    # Specify the engine (= package)
    set_engine("ranger") %>% #specifying "ranger" as the engine/package to run random forest 
    # Specifying mode  
    set_mode("regression") #random forest can handle both regression (when y is numerical) and classification (when y is categorical) #Here, we are specifying "set_mode("regression")" because our y variable is numerical [continuous]

>>>>

Note: the following code chunk would not work if "tree_depth" and "learn_rate" were not fine tuned in the "xgb_spec" object.

@@

#parallel processing
registerDoParallel(cores = parallel::detectCores()-1) #starts parallel processing

@@

stopImplicitCluster() #ends parallel processing

@@

```{r final_spec_fit}
final_spec <- boost_tree(
  trees = best_r2$trees,           # Number of boosting rounds (trees)
  tree_depth = best_r2$tree_depth #, # Maximum depth of each tree
  #min_n = best_r2$min_n,           # Minimum number of samples to split a node
  #learn_rate = best_r2$learn_rate  # Learning rate (step size shrinkage)
) %>%
  set_engine("xgboost") %>%
  set_mode("regression")

@@

@@

```{r}
final_fit %>%
  collect_predictions() %>%
  ggplot(aes(x = yield,
             y = .pred)) +
  geom_point() +
  geom_abline() +
  geom_smooth(method = "lm") +
  scale_x_continuous() +
  scale_y_continuous() 
```

@@

rf_spec <- 
  # Specifying random forest as our model type, asking to tune the hyperparameters
  rand_forest(trees = tune(),
              mtry = tune(),
              min_n = tune()#both "trees" and "mtry" are model-type level hyperparameters, meaning that we fine tune "trees" and "mtry" inside "rand_forest()"
              ) %>%
    # Specify the engine (= package)
    set_engine("ranger") %>% #specifying "ranger" as the engine/package to run random forest 
    # Specifying mode  
    set_mode("regression") #random forest can handle both regression (when y is numerical) and classification (when y is categorical) #Here, we are specifying "set_mode("regression")" because our y variable is numerical [continuous]
